---
title: "HW 3"
author: "Name here"
output: html_document
---

Please use D2L to turn in both the HTML output and your R Markdown file in.

## Q1. R style guide (4 pts)
Summarize what you learned from the [Google R style guide](https://google.github.io/styleguide/Rguide.xml).

## Q2. Course Overview (2 pts)

### a. (1 pt) 
What has been your favorite thing about this course so far?

### b. (1 pt) 
What (if anything) could be changed in this course to improve your learning?


## Q3. Writing Functions (4 pts)

Write a function that:

- takes a integer and 
- returns TRUE if a value is even 

Note the modulus operator `%%` is useful. This is the remainder for division, so this provides an easy way to test whether an integer is even or odd as 7 %% 2 is `r 7 %% 2` and 8 %% 2 is `r 8 %% 2`.
```{r func}
#is.even <- function(val){
#  remainder <- val %% 2 == 1
#}
```


## Q4. Creating Tables (4 pts)

Download the Housing dataset at: [http://math.montana.edu/ahoegh/teaching/stat408/datasets/HousingSales.csv](http://math.montana.edu/ahoegh/teaching/stat408/datasets/HousingSales.csv). Compute the average home price across the states in the dataset. Print the results to a table using the `kable` function.

Also write a sentence that describes the average housing price in Montana and use R Markdown's inline tools to include the price in a sentence.

## Q5. 
Evaluate the following R code and provide a written explanation for each piece of code.

```{r function,eval=F}
ski <- data.frame(ski.hill = c('Bridger Bowl','Big Sky','Red Lodge Mtn'), 
                  new.snow = c(TRUE,FALSE,TRUE),
                  acres = c(2000, 5800, 1600 ))
```

### a. (1 point)
```{r eval=F}
ski[1, 1]
```
 
 \vfill
 \vfill
 
### b. (1 point)
```{r eval=F}
subset(ski, new.snow == TRUE)
```

\vfill
\vfill

### c. (1 point)
```{r eval=F}
max(ski$acres)
```

\vfill
\vfill

